Data Management for LSST Special Programs

### 2023-10-18 sec_intro.tex
Update sec_intro.tex

\item All visits should have both a region and a program label.
These labels should be propagated to all derived data products, such as
processed images, catalog data, and alerts. (Section~\ref{ssec:sci_labels})

\item All visits that \emph{can} be processed by the Prompt pipelines and generate 
alerts \emph{should} be, in support of time domain and Solar System science goals. (Section~\ref{ssec:proc_wfd})

\item Special Processing to create ``unique and separate" data products for Special Programs
should be done when it is possible and necessary, as defined in Section~\ref{ssec:proc_rdm}.

@@

Special Programs are typically driven by specific science goals that build on or 
add to the core science pillars of the LSST.

About 10--15\% of the total 10-year LSST time-span will be spent obtaining 
observations associated with Special Programs.
Special Programs includes non-WFD LSST components such as the Deep Drilling 
Fields (DDFs) and the mini-, micro-, and nano-surveys \citedsp{PSTN-055}.

@@

The DDFs will require Special Processing (Section~\ref{ssec:proc_rdm})
and may also benefit from User-Generated Processing.

@@

The sky areas of mini-surveys can be within, adjacent to, or detached from the WFD footprint.
Mini-surveys can have non-standard visits.

For a list of the mini-surveys under consideration,
see \citeds{PSTN-055}.

Most mini-surveys are likely to require Special Processing (to be considered on a case-by-case basis),
and some are also likely to require User-Generated Processing.

>>>>

\item All visits should have a region label \textit{and} a program 
label, and these labels should be propagated to processed images and catalog data.
(Section~\ref{ssec:sci_labels})

\item Special Processing should be done by Rubin Data Management to 
produce unique and separate (but joinable) data products
for Special Programs when it is both possible and necessary.
(Section~\ref{ssec:sci_sproc}).

\item All visits that \emph{can} be processed by the Prompt pipelines and generate 
alerts \emph{should} be, in support of time domain and Solar System science goals.
(Section~\ref{ssec:sci_pproc})

@@

Special Programs are typically driven by specific science goals that build on or 
add to the core science pillars of the LSST.
They include non-WFD LSST components such as the Deep Drilling 
Fields (DDFs) and the mini-, micro-, and nano-surveys \citedsp{PSTN-055}.
About 10--15\% of the total 10-year LSST will be spent obtaining 
observations associated with Special Programs.

@@

Processing for the DDF images is likely to be a combination of regular (Prompt) processing,
Special Processing, and User-Generated Processing.

@@

The sky areas of mini-surveys can be within, adjacent to, or detached from the WFD footprint.
Mini-surveys can have non-standard visits.
Target-of-opportunity observations for, e.g., the discovery of optical counterparts to 
multi-messenger astrophysical phenomena, are considered a type of mini-survey in this document.
For a list of the mini-surveys under consideration,
see \citeds{PSTN-055}.

Processing for the mini-surveys is likely to be a combination of regular (Prompt) processing,
Special Processing, and User-Generated Processing.
